---
title: "Data Processing Overview"
author: "Dave Lovell"
date: "20/02/2020"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message = FALSE, warnings = FALSE}
require("here")
require("rmarkdown")
```

Hello. If you're looking at this from inside RStudio, just hit `Ctrl+Shift+K` to knit the html. 

We are here: `r here()`

## Render Markdowns Until an error is encountered

### Render Markdown 1 (Initialise Directories)

#### Aim:

Create folder structure (if necessary)

```{r renderMarkdown1, results = "hide", message=FALSE}
render(here("markdowns/1InitialiseDirectories.Rmd"))
```

### Render Markdown 2 (Check Data)

#### Aim:

```{r renderMarkdown2, results = "hide", message=FALSE}
render(here("markdowns/2checkData.Rmd"))
```

Make sure that the data exists

#### Result:
```{r readRdat2}
if(readRDS(here("data/progressRdats/2.rdat"))){
  continue = TRUE
  writeLines("2checkData.Rmd successfully rendered - the files are where they need to be")
} else {
  continue = FALSE
  writeLines("2checkData.Rmd succesfully rendered, but unable to continue. \"portsmouthLeaders2018\" or \"portsmouthLeaders2019\" were not in the \"data\" directory and a connection to the O drive could not be established. See \"markdowns\\2checkData.html\" for details")
}
```

### Render Markdown 3 (Read excels)

#### Aim:

Read the .xlsx files, concatenate them into a single tibble and save it as `data/generalRdats/leaderResponsesUnclean.rdat"

```{r renderMarkdown3, results = "hide", message=FALSE}
render(here("markdowns/3readExcels.Rmd"))
```
