---
title: "readExcels"
author: "Dave Lovell"
date: "21/02/2020"
output: html_document
---

```{r setup3, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries3, message = FALSE}
library("here")
library("readxl")
library("dplyr")
library("purrr")
library("magrittr")
```

## Create tibble with sheet names and data selections

```{r excelSheet}
excelSheet <- 
  tibble(sheetNames = c("basic info", "motivations", "leadership", "numbers",
                        "tradition", "description", "geography", "mission", 
                        "engage with bible", "worship community", "sacraments",
                        "three self", "stewardship", "disciple evangelism")) %>%
  mutate(skipRows = sheetNames %in% c("motivations", "tradition",
                                      "worship community", "three self",
                                      "disciple evangelism") %>% 
           as.numeric)

excelSheet
```

## Do a two 'readxl's for each row

```{r readExcels, warning = FALSE, cache = TRUE}

excelSheet %<>%
  mutate(
    data2018 = map2(sheetNames, skipRows,
                    ~ {read_excel(
                       here("data/portsmouthLeaders2018.xlsx"),
                       sheet = .x,
                       skip = .y)}),
    data2019 = map2(sheetNames, skipRows,
                    ~ {read_excel(
                       here("data/portsmouthLeaders2019.xlsx"),
                       sheet = .x,
                       skip = .y)}))

# Add abbreviations of column names for ease of cagegorisation::::::::::::
excelSheet %<>%
  mutate(abr = map_chr(sheetNames,
                        ~ switch(.,
                      "basic info" = "info_",
                      "motivations" = "mot_",
                      "leadership" = "lead_", 
                      "numbers" = "num_",
                      "tradition" = "trad_",
                      "description" = "desc_",
                      "geography" = "geog_",
                      "mission" = "mis_",
                      "engage with bible" = "bib_",
                      "worship community" = "wc_",
                      "sacraments" = "sac_",
                      "three self" = "ts_",
                      "stewardship" = "ste_",
                      "disciple evangelism" = "de_")))

excelSheet
```

### Append 'abr' to colnames in each tibble

With the exception of the 'Name of fresh expression' column, which will be used to join later.

```{r renameAllTibs}
excelSheet %<>% 
  ### Prefix each column name with its sheet prefix ::::::::::::
  mutate_at(c("data2018","data2019"),
              ~ map2(.,abr,
                     ~ rename_at(.x,
                                 vars(-contains("Fresh expression name")),
                                  function(m) paste0(unique(.y),m)) %>%
  ### Add a 'sheet' column to each tibble          ::::::::::::
              mutate(sheet = .y)))

excelSheet$data2018[[1]]
```

## Dimension investigation

Which of these tibbles have inconsitent dimensions between years?

```{r lookDims}
filter(excelSheet, sapply(data2018,ncol) != sapply(data2019,ncol))
```

Only 'sacraments' and 'leadership' (hopefully!). These are the sections in which questions were added between 2018 and 2019. 

## Names investigation

### Are the question names consistent?

Are there any names in the 2018 data that don't come up in the corresponding sheet of the 2019 data, or vice-versa?

```{r namesLook}
excelSheet %>% 
  mutate(badnames = map2(data2018, data2019, 
                        ~ {
                          c(names(.x)[!(names(.x) %in% intersect(names(.x),names(.y)))],
                            names(.y)[!(names(.y) %in% intersect(names(.x),names(.y)))])
                        })) %>% 
  filter(sapply(badnames,length) > 1) %>% 
  select(sheetNames, badnames) %>% 
  mutate(what = sapply(badnames,toString)) %T>%
  {pull(., badnames) %>% 
      sapply(print)}
```

There are some, but they represent the additional rows in the 'leadership' and 'sacraments' sheets'

I've just realised that if we're not careful, read_excel will assign non-matching integers to the ends of identical questions which will effectively swap the rows around between the two tranches. I'll fix that now in Excel (the shame!).

`fixInExcel.exe running....`

Good good good, that's all fixed and everything in nice and explicit.

### Are the fresh expression names consistent?

#### fxC that don't appear in every sheet of 2018 data

```{r fxcNameCheck2018}
excelSheet %>% 
  pull(data2018) %>% 
  sapply(function(x) pull(x, `Fresh expression name`)) -> 
  allNames

table(unlist(allNames)) -> namesTable2018

namesTable2018[namesTable2018 != median(namesTable2018)]
```

I think we should keep these responses - see no reason to get rid of partials.

#### fxC that don't appear in every sheet of 2019

```{r fxcNameCheck2019}

excelSheet %>% 
  pull(data2019) %>% 
  sapply(function(x) pull(x, `Fresh expression name`)) -> 
  allNames

table(unlist(allNames)) -> namesTable2019

namesTable2019[namesTable2019 != median(namesTable2019)]
```

None of those. Nice.

## Concatenate Tibbles

Get a big list of all the names from each year:

```{r getNameLists}
# Getting names from names, don't freak out ------------------------
names2018 <- names(namesTable2018)
names2019 <- names(namesTable2019)
```

Do some big joins. Finally going to use purrr's 'reduce' in the wild!

```{r bigTimeJoinery}
#2018 tibble
append(list(tibble(fxc = names2018)),
  excelSheet %>% 
  pull(data2018) %>% 
    sapply(function(x) rename(x, "fxc" = "Fresh expression name"))) %>% 
  reduce(~{left_join(.x,.y, by = "fxc")}) ->
  leaderResponse2018

append(list(tibble(fxc = names2019)),
  excelSheet %>% 
  pull(data2019) %>% 
    sapply(function(x) rename(x, "fxc" = "Fresh expression name"))) %>% 
  reduce(~{left_join(.x,.y, by = "fxc")}) ->
  leaderResponse2019

head(leaderResponse2018[,1:6], 10)
head(leaderResponse2019[,1:6], 10)
```

## Concatenate concatenated tibbles into single tidy tibble

```{r superTidy}
leaderResponse2018 %<>% mutate(tranche = factor(2018, 
                                                levels = c(2018,2019,2020),
                                                ordered = TRUE))
leaderResponse2019 %<>% mutate(tranche = factor(2019, 
                                                levels = c(2018,2019,2020),
                                                ordered = TRUE)) 

sharedNames = intersect(names(leaderResponse2018), names(leaderResponse2019))

notIn2019 = names(leaderResponse2018)[!(names(leaderResponse2018) %in% sharedNames)]
notIn2018 = names(leaderResponse2019)[!(names(leaderResponse2019) %in% sharedNames)]

addRowsMatrix <- matrix(NA, nrow = nrow(leaderResponse2018), ncol = length(notIn2018))
colnames(addRowsMatrix) = notIn2018

addRowsMatrix %<>% as_tibble
leaderResponse2018 %<>% cbind(addRowsMatrix)

addRowsMatrix <- matrix(NA, nrow = nrow(leaderResponse2019), ncol = length(notIn2019))
colnames(addRowsMatrix) = notIn2019
addRowsMatrix %<>% as_tibble

leaderResponse2019 %<>% cbind(addRowsMatrix)

rbind(leaderResponse2018, leaderResponse2019) ->
  leaderResponses

head(leaderResponses)
```

