---
title: "4cleanData"
author: "Dave Lovell"
date: "24/02/2020"
output: html_document
---

```{r setup4, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries4, message = FALSE, warning = FALSE}
library("dplyr")
library("magrittr")
library("tidyr")
library("purrr")
library("stringr")
library("lubridate", pos = 20)
library("here") # NB 'here' and 'lubridate' don't interact well, so this needs to go last.
```
## Clean the Data

Make it real good yeah.


### Read the unclean data

```{r readUnclean}
responses <- 
  readRDS(here::here("data/generalRdats/leaderResponsesUnclean.rdat"))

nrow(responses)
ncol(responses)
```

### Rename the columns

#### Catch old names

```{r catchNames}
oldNames <- names(responses)
```

NB put the below together with `paste0(" = \"", names(responses),"\", ") %>% writeClipboard`

#### Rename
```{r renameCols}
responses %<>%
  rename("info_stillMeeting" = "info_Is this fresh expression/church plant still meeting?", 
"fxc" = "fxc", 
"info_deanery" = "info_Deanery", 
"info_sendingChurch" = "info_Name of Sending Church", 
"info_venueDetails" = "info_Normal meeting place name, address and website (if any)", 
"info_startDate" = "info_Start", 
"info_newFurther" = "info_New and further group?", 
"info_anglican" = "info_Anglican or Anglican partner?", 
"info_howMissional" = "info_Describe how you tried to engage with non-church goers", 
"info_isChurch" = "info_Church in its own right?", 
"info_frequency" = "info_How often do you meet?", 
"info_days" = "info_Which day (s)", 
"info_startTime" = "info_Start time", 
"info_endTime" = "info_End time", 
"info_description" = "info_Please describe your fxC", 
"info_relativeLocation" = "info_WHERE is the fresh expression planted in relation to the “sending” church? Tick only one box", 
"mot_bishopOrDiocesan" = "mot_Bishop / diocesan initiative", 
"mot_churchShouldGrow" = "mot_Grow is what Church should do", 
"mot_inadequatePenetration" = "mot_Inadequate penetration of the parish", 
"mot_newHousing" = "mot_New housing opportunity", 
"mot_physicallyRestricted" = "mot_Physically restricted at sending church", 
"mot_increaseDiversity" = "mot_Provide increased diversity", 
"mot_unreachedGroup" = "mot_Unreached people group", 
"mot_other" = "mot_Other", 
"mot_otherDetail" = "mot_...10", 
"lead_name" = "lead_Name of leader", 
"lead_address" = "lead_Address", 
"lead_email" = "lead_Email address", 
"lead_phone" = "lead_Phone number", 
"lead_teamSize" = "lead_Number of people on leadership team", 
"lead_office" = "lead_Office", 
"lead_payStatus" = "lead_Pay Status", 
"lead_time" = "lead_Time", 
"lead_gender" = "lead_Gender", 
"train_msm" = "lead_Mission shaped ministry", 
"train_msi" = "lead_Mission shaped introductions", 
"train_plantingModule" = "lead_Planting module", 
"train_trainingEvent" = "lead_Training event", 
"train_consultancy" = "lead_Consultancy provided", 
"train_fxcExperience" = "lead_Previous fresh expression experience", 
"train_non" = "lead_None", 
"train_other" = "lead_Other", 
"num_sentAdults" = "num_Number of adults sent to begin FxC", 
"num_sentChildren" = "num_Number of children sent to begin FxC", 
"num_averageAdults" = "num_Average attendance adults", 
"num_averageChildren" = "num_Average attendance children", 
"num_averageAttendance" = "num_Total average attendance", 
"num_wc" = "num_Total Fresh Expression worshipping community (all people who would consider themselves part of the fresh expression)", 
"num_volunteers" = "num_Estimated number of members actively volunteering for the Fresh Expression",
"trad_angloCatholic" = "trad_Anglo-Catholic", 
"trad_central" = "trad_Central", 
"trad_charismatic" = "trad_Charismatic", 
"trad_evangelical" = "trad_Evangelical", 
"trad_liberal" = "trad_Liberal", 
"df_denominationalFeatures" = "trad_Denominal features", 
"bui_type" = "trad_Ecclesical / Secular / House", 
"bui_ownership" = "trad_Owned / Rented / Loaned", 
"bui_license" = "trad_Licensed for public worship / Unlicensed", 
"bui_variety" = "trad_Variety of locations used?", 
"bui_legalStatus" = "trad_What legal status?", 
"desc_allAge" = "desc_All age worship", 
"desc_alternative" = "desc_Alternative worship", 
"desc_cafe" = "desc_Café Church", 
"desc_cell" = "desc_Cell Church", 
"desc_childFocused" = "desc_Child Focused Church", 
"desc_underFives" = "desc_Church based on <5s", 
"desc_cluster" = "desc_Cluster based Church", 
"desc_cdp" = "desc_Communiuty Development Plant", 
"desc_messy" = "desc_Messy Church", 
"desc_midweek" = "desc_Midweek Chuch", 
"desc_multipleSunday" = "desc_Multiple Sunday congeration", 
"desc_network" = "desc_Network Church", 
"desc_newMonastic" = "desc_New Monastic", 
"desc_olderPeople" = "desc_Older People's Church", 
"desc_schoolBased" = "desc_School based Church", 
"desc_seeker" = "desc_Seeker Church", 
"desc_tradPlant" = "desc_Traditional Church Plant", 
"desc_newTradService" = "desc_New Traditional service", 
"desc_youthChurch" = "desc_Youth Church", 
"desc_other" = "desc_Other", 
"desc_otherDetail" = "desc_Special Interest group: e.g. Arts/Goths/workplace/helping addicts/learning disability. Describe it", 
"geog_expandedVillage" = "geog_Expanded village", 
"geog_rural" = "geog_Rural", 
"geog_localAuthorityEstate" = "geog_Local authority estate", 
"geog_privateEstate" = "geog_Private estate", 
"geog_suburb" = "geog_Suburb", 
"geog_town" = "geog_Town", 
"geog_cityCentre" = "geog_City centre", 
"geog_localAndPrivateEstate" = "geog_Local and private estate", 
"geog_urban" = "geog_Urban", 
"geog_urbanPriorityArea" = "geog_Urban priority area", 
"geog_newTown" = "geog_New town", 
"geog_other" = "geog_Other", 
"dive_typicality" = "geog_How typical are the people in your Fresh Expression of the social area(s)/context?", 
"dive_diversity" = "geog_How ethnically diverse is your fresh Expression?", 
"netNei_taskNeighbourhood" = "mis_Mission task neighbourhood", 
"netNei_taskNetwork" = "mis_Mission task network", 
"netNei_resultNeighbourhood" = "mis_Result through neighbourhood", 
"netNei_resultNetwork" = "mis_Result through network", 
"mis_taskChr" = "mis_Mission task - Christians", 
"mis_taskDe" = "mis_Mission task - de-churched", 
"mis_taskNon" = "mis_Mission task - non-churched", 
"mis_chr" = "mis_Christians %", 
"mis_de" = "mis_De-churched %", 
"mis_non" = "mis_Non-churched %", 
"pp_pioneer" = "mis_Pioneer work", 
"pp_progression" = "mis_Progression", 
"mis_dynamic" = "mis_Mission support dynamic", 
"bib_sermonTalk" = "bib_Sermon/Talk", 
"bib_passages" = "bib_Passages read in public", 
"bib_groupStudy" = "bib_Study in groups", 
"bib_atHome" = "bib_Encourage individual reading at home", 
"bib_memoryVerses" = "bib_Memory verses", 
"bib_storyTelling" = "bib_Story telling", 
"bib_creative" = "bib_Creative activity / resource", 
"bib_other" = "bib_Other", 
"bib_notAtThisStage" = "bib_Not at this stage yet", 
"wor_worshipBand" = "wc_Worship band", 
"wor_congregationalSinging" = "wc_Congregational singing", 
"wor_artDramaPoetry" = "wc_Art / Drama / Poetry", 
"wor_musically" = "wc_Musically", 
"wor_openPrayer" = "wc_Open Prayer", 
"wor_bibleReading" = "wc_Bible reading", 
"wor_sermon" = "wc_A sermon or talk", 
"wor_intercessions" = "wc_Intercessions", 
"wor_healing" = "wc_Healing ministry", 
"wor_communion" = "wc_Communion", 
"wor_craft" = "wc_Craft activities", 
"wor_food" = "wc_Sharing food", 
"wor_actsKindness" = "wc_Acts of kindness and generosity", 
"wor_blessings" = "wc_Blessings", 
"wor_practiseDisciples" = "wc_Practice as disciples in the community", 
"wor_storiesGodAtWork" = "wc_Telling stories of God at work in lives", 
"wor_silence" = "wc_Silence", 
"wor_other" = "wc_Other...19", 
"wor_otherDetail" = "wc_...20", 
"com_spaceToChat" = "wc_Space and time to chat", 
"com_refreshements" = "wc_Offer refreshments", 
"com_hospitatlity" = "wc_Good hospitality", 
"com_socialMedia" = "wc_Social media", 
"com_activeWebsite" = "wc_An active website", 
"com_specialEvents" = "wc_Special events", 
"com_meal" = "wc_Share in a meal", 
"com_socialActivities" = "wc_Social activities", 
"com_socialAction" = "wc_Social action projects", 
"com_notYet" = "wc_Not yet", 
"com_other" = "wc_Other...31", 
"sac_communion" = "sac_Communion services?", 
"sac_communionFrequency" = "sac_If yes how frequently? (communion)", 
"sac_agape" = "sac_Agape?", 
"sac_baptisms" = "sac_Baptisms?", 
"sac_adultBaptisms" = "sac_If yes number of adults (baptism)", 
"sac_childBaptisms" = "sac_If yes number of children (baptism)", 
"sac_confirmations" = "sac_Confirmations?", 
"sac_adultConfirmations" = "sac_If yes number of adults (confirmation)", 
"sac_childConfirmations" = "sac_If yes number of children (confirmation)", 
"sac_whyNotCommunion" = "sac_If no why? - Communion", 
"sac_whyNotBaptisms" = "sac_If no why? - Baptism", 
"sac_whyNotConfirmations" = "sac_If no why? Confirmation", 
"sac_whoPresidesCommunion" = "sac_If yes who presides? - Communion", 
"sac_whoPresidesBaptism" = "sac_If yes who presides? - Baptism", 
"ts_finacing" = "ts_Self-financing", 
"ts_governing" = "ts_Self-governing", 
"ts_reproducing" = "ts_Self-reproducing", 
"ts_notAtThisStage" = "ts_Not at this stage yet", 
"sf_collections" = "ts_Collections / Donations", 
"sf_regualar" = "ts_Regular giving / standing orders", 
"sf_coverRunning" = "ts_Cover running costs", 
"sf_coverAllCosts" = "ts_Cover all costs (inc. staff)", 
"sf_intentionOnly" = "ts_Intention Only", 
"sf_other" = "ts_Other (self financing)", 
"sg_leadershipTeam" = "ts_Leadership team", 
"sg_legalStructure" = "ts_Formal legal structure", 
"sg_informalPcc" = "ts_Informal PCC representation", 
"sg_formalPcc" = "ts_Formal PCC representation", 
"sg_intentionOnly" = "ts_Intention only...16", 
"sg_other" = "ts_Other (self-governing)", 
"sr_indigenousLeaders" = "ts_Indigenous leaders", 
"sr_enabledElsewhere" = "ts_Enabled reproduction elsewhere", 
"sr_furtherFxc" = "ts_Started further fresh expressions", 
"sr_furtherOutreach" = "ts_Started further outreach", 
"sr_ordinand" = "ts_Ordinand", 
"sr_newBelievers" = "ts_New believers", 
"sr_virtuousLives" = "ts_More virtuous lives", 
"sr_intentionOnly" = "ts_Intention only...25", 
"sr_other" = "ts_Other (self-reproducing)", 
"sr_otherDetail" = "ts_...27", 
"ste_financialResponsibility" = "ste_Which is responsible for the finance of the fxC?", 
"ste_incomeStreams" = "ste_What are the current income streams that enable the Fresh Expression to fund its activities & how much was received through each element during  the last financial year (Jan –Dec )?", 
"ste_surplus" = "ste_What was the level of surplus or deficit for the Fresh Expression in the last financial year?", 
"ste_givers" = "ste_How many people contribute financially to the Fresh Expression?", 
"ste_plannedGivers" = "ste_Of those people detailed at point 3, how many are planned givers (ie in a committed way each week/month to the fresh expression)", 
"ste_fxcExclusively" = "ste_Of those planned givers, how many are only giving to the fresh expression and how many are existing parish planned givers?", 
"ste_supportFromCongregation" = "ste_How much financial support is there from  the main congregation members?", 
"ste_opportunitiesCommunicate" = "ste_The intended message is that people can participate at no cost while there being opportunities to give.  What opportunities are there to give and how are these communicated?", 
"ste_howBuildStewardship" = "ste_What steps have been taken already to build in stewardship principles in terms of time, talents and money into the fresh expression activities?", 
"ste_plansSustainibility" = "ste_What plans and strategy is there to ensure financial sustainability over the next 2-3 years and 3-5 years?", 
"ste_decisionResponsibility" = "ste_Which is responsible for the decision-making and reporting of the fxC?", 
"dis_smallGroups" = "de_Small groups", 
"dis_oneToOne" = "de_One-to-one", 
"dis_courses" = "de_Running courses", 
"dis_serving" = "de_Serving in teams", 
"dis_notAtThisStage" = "de_Not at this stage yet (discipleship)", 
"dis_other" = "de_Other (discipleship)", 
"eva_course" = "de_Enquirers course", 
"eva_relationships" = "de_Building relationships with others", 
"eva_membersShareStories" = "de_Members share their story", 
"eva_inviteWorship" = "de_Inviting to worship", 
"eva_inviteEvents" = "de_Inviting to events", 
"eva_service" = "de_Acts of service", 
"eva_notAtThisStage" = "de_Not at this stage yet (evangelism)", 
"eva_other" = "de_Other (evangelism)", 
"tranche" = "tranche", 
"lead_name2" = "lead_Name of leader 2", 
"lead_email2" = "lead_Email address 2", 
"lead_phone2" = "lead_Phone number 2", 
"lead_name3" = "lead_Name of leader 3", 
"lead_email3" = "lead_Email address 3", 
"lead_phone3" = "lead_Phone number 3")
```

### Document names

```{r nameDocument}
saveRDS(tibble(oldNames,
               names(responses)),
        here::here("data/generalRdats/names.rdat"))
```

## Assign variable types


### Logicals

Many sections of the survey can be intepreted as logicals. Test this:

```{r findLogicals}
responses %>% 
  mutate_all(as.character) %>% 
  select(contains("mot_"),
         contains("train_"),
         contains("trad_"),
         contains("desc_"),
         contains("geog_"),
         contains("bib_"),
         contains("wor_"),
         contains("com_"),
         contains("ts_"),
         contains("sf_"),
         contains("sg_"),
         contains("sr_"),
         contains("dis_"),
         contains("eva_"),
         -contains("other"),
         -contains("notAtThisStage")) %>% 
  pivot_longer(everything()) %>% 
  pull(value) %>% 
  unique 
```
These fields can all be interpreted as logicals with `!is.na(x)`, after turning the `0`s into `frogs`/`NA`s.

Note that because these were multiple choice questions, which means we must treat 'blank' responses as `FALSE`. 

```{r makeLogicals}
responses %<>% 
  mutate_at(vars(contains("mot_"),
         contains("train_"),
         contains("trad_"),
         contains("desc_"),
         contains("geog_"),
         contains("bib_"),
         contains("wor_"),
         contains("com_"),
         contains("ts_"),
         contains("sf_"),
         contains("sg_"),
         contains("sr_"),
         contains("dis_"),
         contains("eva_"),
         -contains("other"),
         -contains("notAtThisStage")),
         ~ {as.character(.) %>% 
             replace(.=="0",NA)} %>% 
             (negate(is.na)))
```

### Numerics

Likewise, the 'num' section can be intepreted as numerical:

```{r make testNumericals}
responses %>%
  mutate_all(as.character) %>% 
  select(contains("num_")) %>% 
  pivot_longer(everything()) %>% 
  pull(value) -> numVals

numVals[!is.na(numVals)&str_detect(numVals,"\\D")]

```
U hate 2 c it. What's to be done about these? I'm goint to make them all into NAs, except the two with numbers in, which I will extract the numbers from.

```{r mutateBadNums}
responses %<>% 
  mutate_at(vars(contains("num_")),
            function(x){
              as.character(x) %>% 
                map_dbl(~ {
                  if(is.na(.)|str_detect(.,"\\d",negate = TRUE)) return(NA)
                  else{
                    tmp <- str_extract(.,"\\d+") %>% as.numeric
                    return(tmp)}
                    
                    
                })})

```

### Factors

Non-ordered factors are easy:

```{r makeFactors}
responses %<>%
  mutate_at(c("info_deanery", "lead_gender", "df_denominationalFeatures",
              "bui_type", "bui_ownership", "bui_license", "bui_legalStatus",
              "mis_dynamic", "sac_whoPresidesCommunion"), as.factor) 

# This one needs a little handling:
responses %<>%
  mutate(sac_whoPresidesBaptism = 
           sac_whoPresidesBaptism %>% 
           str_trim %>% 
           replace(.=="Clergy member of the fresh expression",
                   "Clergy members of the fresh expression") %>% 
           as.factor)
```

Ordered factors take a little longer:


```{r makeOrderedFactors}
responses %<>%
  mutate(info_frequency = 
           info_frequency %>% 
           factor(levels = c("Weekly", "Fortnightly", "Monthly"),
                  ordered = TRUE),
         info_days = 
           info_days %>% 
           factor(levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"),
                  ordered = TRUE),
         lead_payStatus = 
           lead_payStatus %>% 
           factor(levels = c("Voluntary", "Locally paid", "Stipendiary"),
                  ordered = TRUE),
         lead_time = 
           lead_time %>%
           str_replace_all("-"," ") %>% 
           str_to_title %>% 
           factor(levels = c("Spare Time", "Part Time", "Full Time"),
                  ordered = TRUE),
         dive_typicality = 
           dive_typicality %>% 
           factor(levels = c("Slightly", "Moderately", "Mainly", "Totally"),
                  ordered = TRUE), 
         dive_diversity = 
           dive_diversity %>%
           replace(.=="Noone with ethnic background at present",
                   "One ethnic background") %>% 
           replace(.=="None at present",
                   "One ethnic background") %>% 
           factor(levels = c("Prefer not to say", "One ethnic background",
                             "A few ethnic backgrounds",
                             "Wide diversity of ethnic backgrounds")),
         )

```

### More complicated logicals

Some logicals will take a little more cleaning. Also included here are any logicals which cannot be capture by their `"$.+_"` prefix.

```{r cleanComplicatedLgl}
responses %<>%
  mutate_at(c("bib_notAtThisStage", "dis_notAtThisStage", "eva_notAtThisStage",
              "ts_notAtThisStage", "info_anglican", "sac_agape",
              "sac_baptisms", "sac_communion", "sac_confirmations", "info_stillMeeting",
              "info_newFurther", "info_isChurch", "mot_other", "desc_other",
              "wor_other", "sr_other"), 
            ~ str_to_lower(.) %>% 
              str_trim %>% 
              replace(.=="1", "TRUE") %>% 
              replace(.=="0", "FALSE") %>% 
              replace(.=="yes", "TRUE") %>% 
              replace(.=="no", "FALSE") %>% 
              replace(.=="at present leader does not see this happening.  some leaders are uncomfortable even asking for donations", "FALSE") %>% 
              replace(.=="i see it as a separate service within st peter's", "FALSE") %>%               replace(.=="personally yes, but many could say no!", "TRUE") %>%
              replace(.=="yes but only just", "TRUE") %>% 
              replace(.=="yes and no", "NA") %>% 
              replace(.=="0.01", "FALSE") %T>%  # Have these people never completed a survey before? Rounding this down lol
              {if(!all(. %in% c("TRUE","FALSE", "NA", NA))){
                writeLines("Bad data! Possible data loss if coerced to logical!")
                print(.[!(. %in% c("TRUE","FALSE", "NA", NA))])
              }} %>% 
              as.logical)
```

#### com_other

This field is complicated - it's treated differently accross tranches. 

```{r fixComOther}
unique(responses$com_other)

responses %<>%
  mutate(com_otherDetail = 
           replace(com_other,com_other=="1",NA),
         com_other = !is.na(com_other))

```


### Mission / network / neighbourhood numerics

These are pretty trivial

```{r netNeiEtc}
responses %>% 
    select(contains("mis_Task"), contains("netNei_"),
           contains("sac_adultBaptisms"), contains("sac_childBaptisms")) %>%
      mutate_all(as.character) %>% 
      pivot_longer(everything()) %>% 
      pull(value) %>% 
      unique %>% 
      print
    
    writeLines("Those can all be handled by extracting any numbers and casting to numeric.
               The warnings below are good - the coercion is the objective here.")

  responses %<>% 
    mutate_at(vars(contains("mis_Task"),contains("netNei_"),
                   contains("sac_adultBaptisms"), contains("sac_childBaptisms")),
              ~ as.character(.) %>%
                str_extract("\\d+") %>% 
                as.numeric)

```

### Why not baptisms / confirmations / communion

These are encoded in an unusual way, and will need to become multiple fields to preserve tidy priniciples.

```{r tidyWhyNots}
responses %>% 
  select(contains("sac_whyNot")) %>% 
  pivot_longer(everything()) %>% 
  pull(value) %>% 
  unique

responses %<>%
  mutate(sac_bapNotAtThisStage =
           (str_detect(sac_whyNotBaptisms, "Not at this stage"))|(str_detect(sac_whyNotBaptisms, "Not at that stage")),
         sac_bapDontSeeTheNeed = 
           str_detect(sac_whyNotBaptisms,"Don't see the need"),
         sac_bapImpractical = 
           str_detect(sac_whyNotBaptisms, "Impractical")|str_detect(sac_whyNotBaptisms, "Impratical"), # Not very pratical
         sac_bapLackOfAuthorised = 
           str_detect(sac_whyNotBaptisms, "Lack of authorised person"))

responses %<>%
  mutate(sac_conNotAtThisStage =
           (str_detect(sac_whyNotConfirmations, "Not at this stage"))|(str_detect(sac_whyNotConfirmations, "Not at that stage")),
         sac_conDontSeeTheNeed = 
           str_detect(sac_whyNotConfirmations,"Don't see the need"),
         sac_conImpractical = 
           str_detect(sac_whyNotConfirmations, "Impractical")|str_detect(sac_whyNotConfirmations, "Impratical"), # Not very pratical
         sac_conLackOfAuthorised = 
           str_detect(sac_whyNotConfirmations, "Lack of authorised person"))

responses %<>%
  mutate(sac_comNotAtThisStage =
           (str_detect(sac_whyNotCommunion, "Not at this stage"))|(str_detect(sac_whyNotCommunion, "Not at that stage")),
         sac_comDontSeeTheNeed = 
           str_detect(sac_whyNotCommunion,"Don't see the need"),
         sac_comImpractical = 
           str_detect(sac_whyNotCommunion, "Impractical")|str_detect(sac_whyNotCommunion, "Impratical"), # Not very pratical
         sac_comLackOfAuthorised = 
           str_detect(sac_whyNotCommunion, "Lack of authorised person"))

## RIP
responses$sac_whyNotBaptisms <- NULL
responses$sac_whyNotCommunion <- NULL
responses$sac_whyNotConfirmations <- NULL

```

### Times

We need to make the times into times. Had to go back into excel to coerce the 2018 data into 'date' format, because the columns weren't behaving consistently. 2019 and 2018 data need to be handled differently here

Oh pluse for the sake of data preservation we'll have to make an entire new column for the single entry there is that pertains to a second meeting
```{r makeDatesNice}
#Momentarily splitting the tibbles by tranche will avoid the complications of using map with conditionals on a dttm object
#
responses %<>%
  {
  mutate(.,
         info_startTime2 =
           str_extract(info_startTime,"(?<=;).+$") %>%
           str_trim,
         info_endTime2 =
           str_extract(info_endTime,"(?<=;).+$") %>% 
           str_trim) %>%
      mutate (info_startTime =
                str_remove(info_startTime,";.+(?=$)"),
              info_endTime = 
                str_remove(info_endTime, ";.+(?=$)")) 
  }

responses %>% 
  group_by(tranche) %>% 
  group_split ->
  splitTibs

# Name these tables
nameVect = c("2018","2019")

if(all(splitTibs[[1]]["tranche"]=="2019")) nameVect %<>% rev

names(splitTibs) = nameVect

### Excel dates have an origin of "1899-12-30", but since these all all just time data I'm going to make them land on the 1st Jan 2020, rather than some time in 1822
splitTibs[["2019"]] %<>% 
  mutate_at(c("info_startTime", "info_endTime",
              "info_startTime2", "info_endTime2"),
            ~ lubridate::as_datetime(as.numeric(.), origin = "2090-01-01"))

## Now the 2019 data, which is different.

splitTibs[["2018"]] %<>%
  mutate_at(c("info_startTime", "info_endTime",
              "info_startTime2", "info_endTime2"), 
           ~ paste0("01/01/2020 ",.) %>% 
            {coalesce(parse_date_time(., "dmy IM p"),
                      parse_date_time(., "dmy I p"))})

responses = rbind(splitTibs[["2018"]], splitTibs[["2019"]])

## Don't worry about those warnings - they're caused by lots of empty values and the trial-and-error approach of coalescing two different parse-formats.
```

### Start date

There's a lot of varity in 'startDate', but most variables are just dates, so may as well abstract to that fidelity to save time.

As such, not going to bother with dateTime objects - may as well just express year as a double.

No on second thoughts, I'll parse the years as date_times, because that may be more compatible with future tranches.

```{r makeStartDateGood}

responses %<>% 
  mutate(info_startDate = 
           info_startDate %>% 
           replace(. == "Unknown, at least 10 years", NA) %>% 
           replace(. == "Jul-11 - Messy Church Feb-18 - All Age Messy Church", "2018") %>% 
           str_remove_all("\\D") %>% 
           str_extract(".{2}(?=$)") %>% 
           {paste0("20",.)} %>% 
           parse_date_time("y"))
```

### lead_teamSize

```{r fixTeamSize}

responses$lead_teamSize %>% {.[!is.na(.)&str_detect(.,"\\D")]} 
#Happy to make that an NA

responses %<>%
  mutate(lead_teamSize =
           as.numeric(lead_teamSize))
  
```

## Check fields

### Low variation character vectors

Character vectors with low variation may need to be factors

```{r limitedResponses}
responses %>%
  select_if(is.character) %>%
  select_if(~ length(unique(.)) < 10) %>%
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  summarise(length(unique(value)),
            toString(unique(value))) %>% 
  arrange (`length(unique(value))`)
```

### All character Vectors

```{r allCharVect}
responses %>% 
  select_if(is.character) %>% 
  glimpse #Much easier
```

I'm not going anywhere near `ste_surplus`. That's about 2 hours of wrangling (or 30 minutes of manual input lol) for data we don't need. 

Likewise I'm going to leave questions about responsibility alone for now, lots of those responses are ugly and I don't know that I'll need to report on them. 

That means it's done! All that remains is to:

## Save RDS

(and csv)

```{r saveCleanedRDAT}
saveRDS(responses, here("data/generalRdats/responses.rdat"))
readr::write_csv(responses, here("data/responses.csv"))
```