---
title: "attendersCleaning"
author: "Dave Lovell"
date: "05/03/2020"
output: html_document
---

```{r setup5, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r libraries5}
library("magrittr")
library("readr")
library("here")
library("dplyr")
library("forcats")
library("stringr")
```
# Cleaning the 2018 Attenders Responses

This should be way easier than the leaders responses - attenders data is already clean. Most of the work will go into correctly interpreting the numerical codes used in the original file.

## Survey Questions

Before we begin, it's worth acknowledging that this data comes from 2 different surveys. To clean it, we'll need to know what questions were used in those surveys.

### Kids survey

|Question|Type|Responses|
|---|---|---|
|Are you a boy or a girl?|Multiple Choice|`Boy` `Girl`|
|How old are you?|Text|`NA`|
|How often do you come to [fxc]?|Multiple Choice|`Almost always` `about half the time` `A few times a year` `This is my first or second time` `I'm just visiting today as a one-off`|
|Before being part of [fxc]...|Multiple Choice|`I was not part of another church because I didn't go to church` `I had a big gap between my last church and being part of [fxc]` `I moved straight to [fxc] from my last church` `I am part of a church as well as [fxc]`|
|Why did you start coming to [fxc]?|Multiple Choice w/ text|`We moved to the area` ` My family or I were part of the team that came to start this church` `My family or I changed church and decided this was better for us` `I stated coming to [fxc] before I was 5 years old` `A different reason (please write it down):`|

### Adults Survey 

|Question|Type|Responses|
|---|---|---|
|Please circle your gender|Multiple Choice|`Female` `Male` `Other`|
|Please circle your age group|Multiple Choice|`11-15` `16-17` `18-24` `25-29` `30-34` `35-44` `45-54` `55-64` `65-74` `75+`|
|Please circle how often you come to Tots in Tow:|Multiple Choice|`Almost always` `About half the time` `A few times a year` `This is my first or second time` `I'm just visiting today as a one-off`|
|What is your ethnic background|Multiple Choice|`White` `Black/African/Caribbean/Black British` `Asian/Asian British` `Other` `I'd prefer not to say`|
|When you started being part of [fxc]...|Multiple Choice /w text|`It was the first church community that I had been a part of` `I was returning after a break (of more than 2 years) from church in general` `I moved straight from another church to being a part of [fxc]` `I am part of a church as well as [fxc]`|
|I started being part of [fxc]...|Multiple Choice /w text|`because I moved to the area` `because I was part of the team that came to start this church` `because I changed church and decided this was better for me` `because I started to attend [fxc] before I was five years old` `because of a different reason (please specify)...`|
|As a child [0-10]...|Multiple Choice|`I was not part of a church community or Sunday school` `I was part of/I stated being part of a church community or a Sunday school` `I was part of a church community of a Sunday school for a while but stopped going during this period`|
|In my teens [11-17]... [0-10]|Multiple Choice|`I was not part of a church or church youth group` `I was part of/I stated being part of a church or church youth group` `I was part of a church or church youth group for a while but stopped going during this period`|
|In my late teens/early 20s [18-24]... [0-10]|Multiple Choice|`I was not part of a church or a christian union` `I was part of/I stated being part of a church or a christian union` `I was part of a church or a christian union for a while but stopped going during this period`|
|As an adult [25+]...|Multiple Choice w/ text|`I was not part of a church community until (please put the year)` `I have been a church goer all my adult life` `I did leave church, but came back in (year of your return)` `it's quite complicated because`|
|Would you identify yourself as a Christian|Multiple Choice|`Yes` `No` `I'm exploring Christianity` `It's complicated`|
|If Yes to Q12, did you become a Christian at [fxc]|Multiple Choice|`Yes` `No, I was already a Christian` `Tots in Tow helped me rediscover a faith I had lost`|


## Read CSV

```{R readTheAttendersCSV, message = FALSE}
attenders <- readr::read_csv(here::here("data/attenders2018Unclean.csv"))
spec(attenders)
```

## Kill Bad Cols

Some of these columns are redundant - probably the vestige of the some other fxc survey.

```{r findBadCols}
attenders %>% 
  select_if(~ length(unique(.)) == 1) %>%
  summarise_all(unique) %>%
  glimpse
```

All those can go

```{r killBadCols}
attenders %<>% select_if(~ length(unique(.)) > 1) 
```

Some of these other columns look well dubious, let's scope them out.

```{r whoDis}
attenders %>%
  summarise_all(~ toString(sample(unique(.), 6, replace = TRUE))) %>% 
  glimpse
```

Actually most of those seem worth keeping. `>10 years` can go, evidently a column derived from other data. Also what are `Class1` and `Class2`?

Ah `class1` and `class2` are 'primary' and 'secondary' classifications respectively (this insight from the data entry interface). `notes` is short for 'Decision Notes' - they document why a particular set of classifications were chosen. 

### >10 years

This never comes up the 2018 report, and it doesn't correspond to any of the survey questions. 

**Be gone!**
```{r beGoneScrub}
attenders %<>% select(-`>10 years`)
```

### Class1

Class 1 corresponds to 'church status' - one of:

|Church Status|Class1|
|---|---|
|Churched|1|
|Grown Up Here|2|
|Complex de-churched|3|
|Complex non-churched|4|
|Simple de-churched|5|
|Simple non-churched|6|

```{r makeFactorClass1}
# 'class1' (no capital) is factor from num vals of 'Class1'
 attenders %<>%
   mutate(class1 = factor(Class1) %>% 
            fct_recode("(Missing)" = "0",
                       "churched" = "1",
                       "grewUp" = "2",
                       "complexDe" = "3",
                       "copmlexNon" = "4",
                       "simpleDe" = "5",
                       "simpleNon" = "6"))

# Drop original column, 'Class1' (with capital C)
attenders %<>% select(-Class1)
```

Counterintuitively, `Complex de-churched`, `Complex non-churched` and `Churched` are all types of `Churched`. In these cases, the 'non' and 'de' labels refer to events that precede arrival at the fxc. Remember that 'churched', 'de-churched' and 'non-churched' labels by default exist in relation to the fxC.

Elspeth tells me that 'Class 1' is human derived. But I belive that, for 'uncomplicated' surveys (without weird written notes), it should be possible to derive these labels with a kind of 'black-box' technique, by matching new data to old and assigning the same `class1` value. Obviously `class1` is going to be renamed. 

NB all this 'working out' is coming from consultation with my colleague Eslpeth and an investigation of the 'Overall attenders survey findings' document ^[O:/WCC/Learning and Development/Research/Archive/Complete PROJECT - Portsmouth 2018/Attenders survey/Overall attenders survey findings.xlsx]

### Class2

`Class2` is about why you started coming to this fxC. Not everybody gets a `class2` - or rather, many people get a `Class2` of 0. You only get a `Class2` > 0 if your `Class1 %in% c(1,3,4)`. That is, only 'churched' people get a `Class2` 

Just reviewing the 2018 attenders report ^[O:/WCC/Learning and Development/Research/Archive/Complete PROJECT - Portsmouth 2018/Reports/Portsmouth attenders survey report 2018.pdf]. It looks like 'reason for joining' is reported either in terms of `class2` for all 'churched' attenders, or in terms of church background for the truly 'de/non-churched' (as well as 'grew up this fxC' people. Ethically dubious that we made some people fill in a question that didn't really apply to them. ~~Anyhow the headline is that `Class2` is not a derived category, unless ignoring a response counts a derivation.~~

Here are the values for class2:

|Transfer Reason|Class2|
|---|---|
|(simple)De/non or grew up here|0|
|Part of the team sent to start this church|1|
|Part of another church as well|2|
|Moved to the area|3|
|This church is better for me|4|
|Family, friends or life patterns|5|
|Simple non-churched|6|


```{r class2IsAFactorNow}
attenders %<>%
  mutate(class2 = factor(Class2) %>% 
           fct_recode("(Missing)" = "0",
                      "team" = "1",
                      "blending" = "2",
                      "moved" = "3",
                      "better" = "4",
                      "family" = "5")) 

attenders %<>% select(-Class2)
```

`class2` is a derived category - it's calculated from the responses to several different questions. Here's how it appears to work:

1. Those who are "truly" non or de churched (or grew up here) are not assigned a `class2`. In the reports, these `class2` `NA`s are functionally coalesced with the church backgrounds column.
2. Those ticking 'I am part of a church as well as [fxc] for **question 6** are assigned `blending`
3. Those who are 'churched' (excluding `grewUp`s) but not 'blending' are assigned another `class2` value, based on their response to **question 7**. Either
  a. Their response is automatically encoded as one of: `team`, `moved` or `better` based on the box they ticked.
  b. Tickers of `because of a different reason (please specify)` are encoded as one of the above (if they are bad at surveys), or dropped into the catch-all category (`family`) of "family, friends, or life patterns".

### fxC Names

We don't actually have fxc names - just ids. Will need to pull another table from the .mdb in order to join them I guess.

## Recode Various things as factors

### Response Type

```{r responseTypeRecode}
# Recode (and rename) -------------------------
attenders %<>%
  mutate(responseType = 
           ResponseType %>% 
           factor %>% 
           fct_recode("child" = "C",
                      "adult" = "A"))
# Drop ----------------------------------------
attenders %<>% select(-ResponseType)
```

### ageGroup

Age group is encoded strangely, mostly out a desire to be careful not to report on under fives (which the diocese wanted to record anyway). `5.4` means 4.

```{r ageGroupRecode}
# Recode (and rename) -------------------------
  
attenders %<>%
  mutate(ageGroup = 
           str_trim(AgeGroup) %>% 
           str_remove("^5\\.") %>% #get rid of strange notation
           {replace(.,str_detect(., "^[0-5]$"),"0-5")} %>% 
           {replace(., str_detect(., "^([6-9]|(10))$"), "6-10")} %>% 
           factor(levels = c("0-5", "6-10", "11-15", "16-17", "18-24",
                             "25-29", "30-34", "35-44", "45-54",
                             "55-64", "65-74", "75+"),
                  ordered = TRUE))
# Drop ----------------------------------------
attenders %<>% select(-AgeGroup)
```

### gender

How are `prefer not to say`s treated in the processing? Hope their not made the same as `NA` (although probably fine if so).

```{r genderGlimpse}
attenders$Gender %>% unique
```

Yes gender is either 'Male', 'Female' or 'NA'

```{r genderRecode}
# Recode (and rename) -------------------------
attenders %<>%
  mutate(gender = 
           factor(Gender) %>% 
           fct_recode("(Missing)" = "N",
                      "female" = "F",
                      "male" = "M"))
# Drop ----------------------------------------
attenders %<>% select(-Gender)
```

### regularity

Again, these vals are taken from the excel sheet in the footnote.

```{r regularityRecode}
# Recode (and rename) -------------------------
attenders %<>%
  mutate(regularity = 
           Regularity %>% 
           factor %>% 
           fct_recode("(Missing)" = "0",
                      "almostAlways" = "1",
                      "halfTheTime" = "2",
                      "fewTimesAYear" = "3",
                      "firstTime" = "4",
                      "visiting" = "5"))
# Drop ----------------------------------------
attenders %<>% select(-Regularity)
```

### transferStatus

Flying blind here - don't think there's any documentation of how these numbers correspond
to responses. But probably safe to assume that things were encoded in the order that they appear on the survey. Then can check with the report. 

But is this the question I think it is?

```{r transferStatusGlimpse}
attenders$TransferStatus %>% unique
```

Yes, only four possible responses. That narrows the field somewhat. Also fits with the assumption that the questions are recorded in survey order. Always very likely.

Going to rename `TransferStatus` to `churchBackground`, because that's really what it's asking for. 

```{r transferStatusRecode}
# Recode (and rename) -------------------------
attenders %<>%
  mutate(churchBackground =
           TransferStatus %>%
           factor %>%
           fct_recode("(Missing)" = "0",
                      "nonChurched" = "1",
                      "deChurched" = "2",
                      "churched" = "3",
                      "blending" = "4"))
# Drop ----------------------------------------
attenders %<>% select(-TransferStatus)
```

Let's check that this corresponds with report findings:

```{r checkChurchBackgrounds}
attenders$churchBackground %>% 
  table %>% 
  {./sum(.) * 100}
```

Ah. This cannot yet be tested - it needs to be tested in conjuction with other responses (because `grewUp` responses need removing.)

### transferReason

Making the same assumptions as above

```{r transferReasonRecode}
# Recode (and rename) -------------------------
attenders %<>%
  mutate(transferReason = 
           TransferReason %>% 
           factor %>% 
           fct_recode("(Missing)" = "0",
                      "moved" = "1",
                      "team" = "2",
                      "better" = "3",
                      "grewUp" = "4",
                      "other" = "5"))
# Drop ----------------------------------------
attenders %<>% select(-TransferReason)
```

Okay. If `grewUp` is about 17% of all `transferReason`s then things are looking good. 

```{r checkingTransferReason}
attenders$transferReason %>% 
  table %>% 
  {round((./sum(.) * 100))}
```

Oh wow - 40% other! 

Wait let's try something else:

```{r somethingElse}
attenders %>%
  filter(class2=="team") %>%
  pull(transferReason) %>%
  unique

attenders %>%
  filter(class2=="team") %>%
  pull(transferReason) %>%
  unique

attenders %>%
  filter(class2=="(Missing)") %>%
  pull(transferReason) %>%
  unique
```

Okay, our assumptions are good. Big relief.

### Life Stages

Rename all of these to suit my own conventions:

```{r renameStages}
attenders %<>%
  rename_at(vars(contains("Status")),
            ~ str_remove(.,"Status") %>% 
              {paste0("status",.)})
```

I'm going to coerce 0 and 9 to NA - one means no response and one means no response required, but none of that needs to be inherent.

Now also make these into factors

```{r makeStatusFactors}
attenders %<>%
  mutate_at(c("statusChild",
               "statusTeen",
               "statusYoung",
               "statusAdult"),
             ~ factor(.) %>% 
              fct_recode("(Missing)" = "0",
                         "(Missing)" = "9",
                         "notPart" = "1",
                         "wasPart" = "2",
                         "stoppedHere" = "3",
                         "complicated" = "4"))
```

Those warning are fine, especially because there are three of them - only `statusAdult` should have `complicated` values. But also good practise to clean them up:

```{r cleaningStageFactors}
attenders %<>%
  mutate_at(c("statusChild",
              "statusTeen",
              "statusYoung",
              "statusAdult"),
            fct_drop)
```

### YearStarted and YearReturned

Let's have these as numerics.

Why are so many of them '1900'? I'll ask Elspeth.

```{r yearsMutation}
attenders$YearStarted %>% table
attenders$yearReturned %>% table


attenders %<>%
  mutate(yearStated = as.integer(YearStarted),
         yearReturned = as.integer(YearReturned))

attenders %<>% select(-YearStarted,-YearReturned) 
```

### University

A slightly ambiguous question - 'I am currently a student' is offered as an alternative to 'Yes' for the question 'Have you attended university?' Is this 'currently a university student?' or a more general definition of studenthood?

```{r universityCleaning}
attenders %<>%
  mutate(higherEducation =
           factor(University) %>% 
           fct_recode("(Missing)" = "0",
                      "university" = "1",
                      "currentlyStudent" = "2",
                      "apprenticeship" = "3",
                      "noneOfThese" = "4"))

attenders %<>% select(-University)
```

### Ethnicity

This encoding is from the previously mentioned `.xlsx` file. It's not the same order as the listing on the survey.

This is why we do things like this now.


```{r cleaningEthnicity}
unique(attenders$Ethnicity)

attenders %<>%
  mutate(ethnicity =
           factor(Ethnicity) %>% 
           fct_recode("(Missing)" = "0",
                      "white" = "1",
                      "black" = "2",
                      "asian" = "3",
                      "mixed" = "4",
                      "other" = "5",
                      "ratherNotSay" = "6"))

attenders %<>% select(-Ethnicity)
```

### Christian

```{r ChristianCleaning}
attenders %<>%
  mutate(christian = 
           factor(`Christian?`) %>% 
           fct_recode("(Missing)" = "0",
                      "yes" = "1",
                      "no" = "2",
                      "exploring" = "3",
                      "complicated" = "4"))

attenders %<>% select(-`Christian?`)
```
### becameHere

```{r becameHereCleaning}
attenders %<>%
  mutate(becameHere =
           factor(`Became Christian here?`) %>%
           fct_recode("(Missing)" = "0",
                      "yes" = "1",
                      "no" = "2",
                      "rediscover" = "3"))

attenders %<>% select(-`Became Christian here?`)
```

## Review

Let's take a look at what's been achieved:

```{r review}
attenders %>% summarise_all(~ toString(sample(unique(.), 6, replace = TRUE))) %>% glimpse
```

Balls. We've got a '5' floating around in `higherEducation`, and a '4' inside `becameHere`. Just as well that we stopped using `fct_explicit_na`.

**Okay**

Elspeth has helped me again - the original database has a very confusing user interface that lets you see the original data. Turns out those 4/5s are an artifact of a quirk of the data entry interface - 0's correspond to nothing having been selected, but 4/5s correspond to the selection of a `none selected` option. Fixed easily enough:

```{r fixingthosefactors}
attenders %<>%
  mutate(christian = 
           fct_recode(christian,
                      "(Missing)" = "5"))

attenders %<>%
  mutate(becameHere = 
           fct_recode(becameHere,
                      "(Missing)" = "4"))
```

Oh there's also a 5 in `higherEducation` and a 6 in `regularity`. These also correspond to 'not answered'.

```{r fixingthosefactorsSomeMore}
attenders %<>%
  mutate(higherEducation = 
           fct_recode(higherEducation,
                      "(Missing)" = "5"))

attenders %<>%
  mutate(regularity = 
           fct_recode(regularity,
                      "(Missing)" = "6"))
```


## Rename

A few fields need renaming for consistency

```{r renamingAFewThings}
attenders %<>%
  rename("responseId" = "ResponseID",
         "plantId" = "PlantID",
         "transferOther" = "TransferOther",
         "complicatedReason" = "ComplicatedReason",
         "note" = "Notes")
```


Also going to drop responseRef - it's a unique identifier for responses within  a particular plant, but it's redundant because 

```{r droppingResponseRef}
attenders %<>%
  select(-ResponseRef)
```

## Look Again

Let's take a comprehensive look at this data:

```{r talkAboutClass}
attenders %>% sapply(class)
```

```{r lookAllUniques}
attenders %>% select_if(~ length(.) > length(unique(.))) %>% sapply(function(x) unique(as.character(x))[1:10])
```

looking good!

## Let's save that data!

```{r saveRDS}

saveRDS(attenders, here::here("data/generalRdats/attenders2018.rdat"))

#also CSV
write.csv(attenders, here::here("data/attenders2018.csv"),
        row.names = FALSE)

```

Also let's save one with no under fives in;

```{r saveNoUnderFives}
saveRDS(attenders %>% 
          filter(!(ageGroup %in% "0-5")),
        here::here("data/generalRdats/attenders2018NoUnderFives.rdat"))

# Also csv

write.csv(attenders %>% 
          filter(!(ageGroup %in% "0-5")),
          here::here("data/attendersNoUnderFives.csv"),
          row.names = FALSE)
```