---
title: "Printing Attender Classification Reasons"
author: "Dave Lovell"
date: "11/03/2020"
output: html_document
---

```{r libraries6}
library("here")
library("magrittr")
library("dplyr")
```

## Attenders Classification Reasons

I think that for most of the attenders data we can black-box a classification from the other results. That is, we can just map existing combinations of results onto classifications and run it backwards on any new data we recieve. 

But there's a catch - some respondents were classified in a particular way because of human interention, sometimes because they wrote in the margins (perhaps?) or selected multiple responses. In short, they were bad at surveys.

We want to be consistent with past practise, so it's important to understand how these cases were processed. Gladly, the processors of this data left plentiful notes. This markdown is just a printing of those notes. 

```{r readInData, message = FALSE, warning = FALSE}
readRDS(here::here("data/generalRdats/attenders2018NoUnderFives.rdat")) ->
  attenders
```

For this exercise, we will only need the `class1`, `class2` and `note` fields.

```{r selectingClassesandNote}
attenders %<>% select(class1, class2, note)
```

We're only interested in attenders with `note` data (shorthand for 'classification notes' in the original data entry interface):

```{r filterOutNoNotes}
attenders %<>% filter(is.na(note))
```

## All permutations of Class

Let's see what permutations of classification data exist within the filtered tibble:

```{r seePermutations}
attenders %>% 
  group_by(class1, class2) %>% 
  summarise %>% 
  arrange
```

Cool. These will be the subtitles for the rest of this file.
